### 2015-05-14 evaluation.tex
fix in evaluation

Using the race-freedom guarantees from \whoop, we managed to significantly accelerate \corral in most of our benchmarks; the best results were achieved using \yieldmr. Figure~\ref{fig:plot} shows that most speedups using \yieldmr are in the range of 1.5--10$\times$; while in ssu100, and pc8736x\_gpio respectively, we achieved a speedup greater than 10$\times$, and 20$\times$ respectively, using a csb of 9. We notice that a higher csb typically results into greater speedups, when exploiting \whoop. This is expected, as a higher csb directly translates into a larger sequentialized program, and thus \whoop has more opportunities to reduce the sequentialization.

>>>>

Using the race-freedom guarantees from \whoop, we managed to significantly accelerate \corral in most of our benchmarks; the best results were achieved using \yieldmr. Figure~\ref{fig:plot} shows that most speedups using \yieldmr are in the range of 1.5--10$\times$; while in ssu100, and pc8736x\_gpio respectively, we achieved a speedup of 12$\times$, and 20$\times$ respectively, using a csb of 9. We notice that a higher csb typically results into greater speedups, when exploiting \whoop. This is expected, as a higher csb directly translates into a larger sequentialized program, and thus \whoop has more opportunities to reduce the sequentialization.
